Normalized expressions

### 2021-03-29 analysis/normalized.Rmd
Update numbers for package normalized expressions

---
title: "Normalized expressions"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  normalized_path: normalized-expressions.csv
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: FALSE
---

@@

@@

Minimized:
```{r}
widespread_minimized <- E_cano %>%
  group_by(minimized) %>%
  summarize(n_call_sites = n_distinct(src_ref), proportion = ratio(n_call_sites, nb_call_sites), n_packages = n_distinct(ev_package), n_operations = round(mean(n_op, na.rm=TRUE), 2), percent_envir = ratio(n_distinct(cur_data()$src_ref[!is.na(cur_data()$envir)]),  n_call_sites), percent_envir_calls = ratio(sum(!is.na(envir)), n())) %>% 
  arrange(desc(n_call_sites))

@@

```{r}
nrows <- 12
r_vec("MinimizedCallSites", nrows, pull(widespread_minimized, n_call_sites))
r_vec("MinimizedPropSites", nrows, pull(widespread_minimized, proportion))
r_vec("MinimizedPackage", nrows, pull(widespread_minimized, n_packages))
r_vec("MinimizedOperations", nrows, pull(widespread_minimized, n_operations))
r_vec("MinimizedPercentEnvir", nrows, pull(widespread_minimized, percent_envir))
```

@@

r("nb non default envir variables percent", ratio(nb_var_symb_ndefault_sites, nb_var_symb_sites))
```

@@

Seems it was a bug: when the explicit argument was `parent.frame()`, it was counted as being the default argument (but it does not have the same semantics as a default argument or as an explicit one though!).

@@

r("function definition sites", nb_fundef_sites)
r("function definition sites percent", ratio(nb_fundef_sites, nb_call_sites))
r("fundef non default envir sites percent", ratio(nb_ndefault_envir_fundef_sites, nb_fundef_sites))
r("generalized function definition sites", nb_generalized_fundef_sites)
r("generalized function definition sites percent", ratio(nb_generalized_fundef_sites, nb_call_sites))
r("generalized funded non default envir sites percent", ratio(nb_ndefault_envir_gen_fundef_sites, nb_generalized_fundef_sites))
```

@@

r("nb assign sites", nb_assigns_call_sites)
r("assign sites percent", ratio(nb_assigns_call_sites, nb_call_sites))
```

@@

r("non default envir assign sites", nb_a_env_call_sites)
r("non default envir assign sites percent", ratio(nb_a_env_call_sites, nb_assigns_call_sites))
```

@@

Now, we can show the mot common minimized expressions when there are more than 2 for one call site:

@@

```{r}
combination_ranking %>%
  filter(cumpercent < 95) %>%
  ggplot(aes(x = fct_reorder(common_minimized, n), y = percent)) + 
  geom_col() + 
  labs(x = "Combinations", y = "%") +
  coord_flip()
  #theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

@@

r("Nb One Minimized", n_one_mini)
r("Nb One Minimized Percent", ratio(n_one_mini, nb_call_sites))
```

@@

r("nb call sites unique actual value", nb_actual_values_sites)
r("call sites unique actual value percent", ratio(nb_actual_values_sites, value_minimized$n_call_sites))
r("median run sites unique actual value", median(only_actual_values$nb_runs, na.rm = TRUE))
r("average run sites unique actual value", mean(only_actual_values$nb_runs, na.rm = TRUE))
r("sd run sites unique actual value", sd(only_actual_values$nb_runs, na.rm = TRUE))
```

@@

r("val one node", n_one_node)
r("val one node percent", ratio(n_one_node, n_val_exprs))
```

@@

r("one val median runs", med_runs)
r("one val average runs", avg_runs)
r("one val sd runs", sd_runs)
```

@@

r("non default envir value percent", ratio(nrow(non_default_envir), nrow(minimized_sites)))
r("non default envir with var percent", ratio(nrow(non_default_with_var), nrow(non_default_envir)))
```

@@

r("nb slot access", nb_slot_sites)
r("slot access percent", ratio(nb_slot_sites, nb_call_sites))
r("generalized slot access", nb_generalized_slot_sites)
r("generalized slot access percent", ratio(nb_generalized_slot_sites, nb_call_sites))
r("ndefault envir slot site", nb_ndefault_envir_slot_sites)
r("ndefault envir slot site percent", ratio(nb_ndefault_envir_slot_sites, nb_generalized_slot_sites))
```

>>>>

---
title: "Normalized expressions"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  normalized_path: normalized-expressions.csv
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

  E_raw <- E_raw %>% mutate(envir_expression = if_else(envir_type == "NULL", "NULL", envir_expression))

@@

Minimized:
```{r}
widespread_minimized <- E_cano %>%
  group_by(minimized) %>%
  summarize(n_call_sites = n_distinct(src_ref), 
            proportion = ratio(n_call_sites, nb_call_sites), 
            n_packages = n_distinct(ev_package),
            n_operations = round(mean(n_op, na.rm=TRUE), 2), 
            percent_envir = ratio(n_distinct(cur_data()$src_ref[!is.na(cur_data()$envir)]),  n_call_sites), 
            percent_envir_calls = ratio(sum(!is.na(envir)), n()), 
            env_diversity = n_distinct(envir), 
            percent_envir_non_parentframe = ratio(n_distinct(cur_data()$src_ref[!is.na(cur_data()$envir) & cur_data()$envir != "parent.frame()"]),  n_call_sites)) %>% 
  arrange(desc(n_call_sites))

@@

```{r}
nrows <- min(12, nrow(widespread_minimized)) # kaggle has less than 12 rows
r_vec("MinimizedCallSites", nrows, pull(widespread_minimized, n_call_sites))
r_vec("MinimizedPropSites", nrows, pull(widespread_minimized, proportion))
r_vec("MinimizedPackage", nrows, pull(widespread_minimized, n_packages))
r_vec("MinimizedOperations", nrows, pull(widespread_minimized, n_operations))
r_vec("MinimizedPercentEnvir", nrows, pull(widespread_minimized, percent_envir))
r_vec("MinimizedPercentEnvirNonParent", nrows, pull(widespread_minimized, percent_envir_non_parentframe))
```

@@

overview_table(
  r("nb symbol var sites", nb_var_symb_sites),
  r("nb symbol var site percent", ratio(nb_var_symb_sites, nb_var_min_sites)),
  r("nb non default envir variables percent", ratio(nb_var_symb_ndefault_sites, nb_var_symb_sites))
)
```

@@

@@

overview_table(
  r("function definition sites", nb_fundef_sites),
  r("function definition sites percent", ratio(nb_fundef_sites, nb_call_sites)),
  r("fundef non default envir sites percent", ratio(nb_ndefault_envir_fundef_sites, nb_fundef_sites)),
  r("generalized function definition sites", nb_generalized_fundef_sites),
  r("generalized function definition sites percent", ratio(nb_generalized_fundef_sites, nb_call_sites)),
  r("generalized funded non default envir sites percent", ratio(nb_ndefault_envir_gen_fundef_sites, nb_generalized_fundef_sites))
)
```

@@

overview_table(
  r("nb assign sites", nb_assigns_call_sites),
  r("assign sites percent", ratio(nb_assigns_call_sites, nb_call_sites))
)
```

@@

overview_table(
  r("non default envir assign sites", nb_a_env_call_sites),
  r("non default envir assign sites percent", ratio(nb_a_env_call_sites, nb_assigns_call_sites))
)
```

@@

With these minimized expressions:

```{r}
minimized_exprs
```

Now, we can show the mot common minimized expressions per site:

@@

```{r}
combination_ranking %>%
  filter(cumpercent < if(nrow(combination_ranking) <= 10) 101 else 95) %>%
  ggplot(aes(x = fct_reorder(common_minimized, n), y = percent)) + 
  geom_col() + 
  labs(x = "Combinations", y = "%") +
  coord_flip()
  #theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

@@

overview_table(
  r("Nb One Minimized", n_one_mini),
  r("Nb One Minimized Percent", ratio(n_one_mini, nb_call_sites))
)
```

@@

overview_table(
r("nb call sites unique actual value", nb_actual_values_sites),
r("call sites unique actual value percent", ratio(nb_actual_values_sites, value_minimized$n_call_sites)),
r("median run sites unique actual value", median(only_actual_values$nb_runs, na.rm = TRUE)),
r("average run sites unique actual value", mean(only_actual_values$nb_runs, na.rm = TRUE)),
r("sd run sites unique actual value", sd(only_actual_values$nb_runs, na.rm = TRUE))
)
```

@@

overview_table(
  r("val one node", n_one_node),
  r("val one node percent", ratio(n_one_node, n_val_exprs))
)
```

@@

overview_table(
  r("one val median runs", med_runs),
  r("one val average runs", avg_runs),
  r("one val sd runs", sd_runs)
)
```

@@

overview_table(
  r("non default envir value percent", ratio(nrow(non_default_envir), nrow(minimized_sites))),
  r("non default envir with var percent", ratio(nrow(non_default_with_var), nrow(non_default_envir)))
)
```

@@

overview_table(
  r("nb slot access", nb_slot_sites),
  r("slot access percent", ratio(nb_slot_sites, nb_call_sites)),
  r("generalized slot access", nb_generalized_slot_sites),
  r("generalized slot access percent", ratio(nb_generalized_slot_sites, nb_call_sites)),
  r("ndefault envir slot site", nb_ndefault_envir_slot_sites),
  r("ndefault envir slot site percent", ratio(nb_ndefault_envir_slot_sites, nb_generalized_slot_sites))
)
```

# Generalized variable access

```{r}
gen_var <- E_cano %>% filter(minimized %in% c("X", "F(X)", "$"))
nb_gen_var_sites <- gen_var %>% pull(src_ref) %>% n_distinct()

overview_table(
  r("generalized var access sites", nb_gen_var_sites),
  r("generalized var access site percent", ratio(nb_gen_var_sites, nb_call_sites))
)
```
